API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
emphasize that preprocessing may involve learning

\texttt{Pipeline} objects chain multiple estimators into a single one. This is
useful since a machine learning workflow typically involves a fixed sequence of
processing steps (e.g., feature extraction, dimensionality reduction, learning
and making predictions). A sequence of $N$ such steps can be combined into a
\texttt{Pipeline} if the first $N-1$ steps are transformers; the last can be
either a predictor, a transformer or both. Conceptually, fitting a pipeline to
a training set amounts to the following recursive procedure: i) when only one
step remains, call its \texttt{fit} method; ii) otherwise, \texttt{fit} the
first step, use it to \texttt{transform} the training set and \texttt{fit} the
rest of the pipeline with the transformed data. The pipeline exposes all the
methods the last estimator in the pipe exposes. That is, if the last estimator
is a predictor, the pipeline can itself be used as a predictor. If the last
estimator is a transformer, then the pipeline is itself a transformer.

>>>>

\texttt{Pipeline} objects chain multiple estimators into a single one. This is
useful since a machine learning workflow typically involves a fixed sequence of
processing steps (e.g., feature extraction, dimensionality reduction, learning
and making predictions), many of which perform some kind of learning.
A sequence of $N$ such steps can be combined into a
\texttt{Pipeline} if the first $N-1$ steps are transformers; the last can be
either a predictor, a transformer or both. Conceptually, fitting a pipeline to
a training set amounts to the following recursive procedure: i) when only one
step remains, call its \texttt{fit} method; ii) otherwise, \texttt{fit} the
first step, use it to \texttt{transform} the training set and \texttt{fit} the
rest of the pipeline with the transformed data. The pipeline exposes all the
methods the last estimator in the pipe exposes. That is, if the last estimator
is a predictor, the pipeline can itself be used as a predictor. If the last
estimator is a transformer, then the pipeline is itself a transformer.
